---
title: "Predicting Cinema Ticket Sales"
date: "`r Sys.Date()`"
author: Andy Chiv
output:
  rmdformats::material:
    self_contained: true
    thumbnails: false
    lightbox: true
    highlight: tango
    cards: false
    fig_width: 12
    fig_height: 8
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning=FALSE, message = FALSE)
options(scipen=999)
```

# Loading library
```{r libraries}
library(interactions)
library(ggplot2)
library(dplyr)
library(readxl)
```

# Dataset on Cinema Ticket Sales 

```{r}
cinemaTicket <- read.csv("https://raw.githubusercontent.com/andychiv/cinema-ticket-sales-analysis/main/cinemaTicket.csv")
```


# Data Wrangling
```{r}
cin <- cinemaTicket
cin <- na.omit(cin)
cin <- cin %>% filter(ticket_use>=0)  # Filter the negative value of ticket_use
cin$ticket_price <- cin$ticket_price/10000
cin <- cin %>% filter(ticket_price <16)  # Filter the negative value of ticket_use
cin$total_sales <- cin$total_sales/10000

```

# Check if there is an association between Sale and Price
```{r}
cin$cSale <- cin$total_sales - mean(cin$total_sales)
cin$cSold <- cin$tickets_sold - mean(cin$tickets_sold)
cin$cPrice <- cin$ticket_price - mean(cin$ticket_price)
cin$cShowTime <- cin$show_time - mean(cin$show_time)

reg <- lm(cSale~cPrice, data=cin)
summary(reg)
```

Small p-value indicates that there is a stong relationship between Price and Sale


# Visualize the association between Price and Sales
```{r}
g <- ggplot(data=cin, aes(x=ticket_price, y=total_sales, color=total_sales)) + geom_point()
g + ggtitle('Association between Ticket Price ($) and Total Ticket Sales ($)') +
  xlab('Ticket Price ($)')+
  ylab('Total Ticket Sales ($)') +
  scale_color_gradient(low="blue", high="red")
  
```


# Using Dichonomous variable

Let's create a variable called firstHalf refering a period between January and June while 
nonFirstHalf is from July to December

## Run a regression model on Sale based on Price interacting with firstHalf
```{r}
cin <- cin %>% mutate(firstHalf= ifelse(month < 7, yes=1, no=0)) 
reg <- lm(cSale~cPrice*firstHalf, data=cin)
summary(reg)
```

## Visualize the association between Sale and Price*firstHalf (Interaction)
```{r}
g <- ggplot(data=cin, aes(x=ticket_price, y=total_sales, color=total_sales)) + geom_point()
g + ggtitle('Association between Ticket Price ($) and Total Ticket Sales ($)') +
  xlab('Ticket Price ($)')+
  ylab('Total Ticket Sales ($)') +
  scale_color_gradient(low="blue", high="red") +
  facet_wrap(~firstHalf)
```


## Run a regression model on Sales based on Price interacting with nonFirstHalf

```{r}
cin <- cin %>% mutate(nonFirstHalf = 1 - firstHalf)
reg <- lm(cSale~cPrice*nonFirstHalf, data=cin)
summary(reg)
```

## Visualize the association between Sale and Price*nonFirstHalf (Interaction)
```{r}
g <- ggplot(data=cin, aes(x=ticket_price, y=total_sales, color=total_sales)) + geom_point()
g + ggtitle('Association between Ticket Price ($) and Total Ticket Sales ($)') +
  xlab('Ticket Price ($)')+
  ylab('Total Ticket Sales ($)') +
  scale_color_gradient(low="blue", high="red") +
  facet_wrap(~nonFirstHalf)
```


# Spotlight Analysis on ShowTime
```{r}
cin$showTimeHi <- cin$cShowTime - sd(cin$cShowTime)   # Shift the data down
reg <- lm(cSale~cPrice*showTimeHi, data=cin)
summary(reg)
```


```{r}
cin$showTimeLo <- cin$cShowTime + sd(cin$cShowTime)   # Shift the data down
reg <- lm(cSale~cPrice*showTimeLo, data=cin)
summary(reg)
```

# Floodlight Analysis

```{r}
fl <- lm(total_sales ~ ticket_price*show_time , data = cin)
johnson_neyman(fl, pred = show_time, modx = ticket_price, mod.range=c(1, 60), alpha = 0.05, line.thickness = 1,plot = TRUE, 
               title = "Johnson-Neyman Plot")
```


# Report

A full report can be found here: 

[Full Report](https://github.com/andychiv/cinema-ticket-sales-analysis/blob/main/Cinema%20Tickets%20Marketing%20Mix%20Report.pdf)








